---
title: "Examples"
author: "You"
date: "August 2025"
output:
  html_document:
    highlight: tango   # for line numbering to work
---




# Control Sequences

This is a basic example demonstrating some features of R Markdown and knitr. 

The value of x is `r round(x <- sqrt(2), 4)` and displayed here.

After the transformation, x is
`r print(exp(asin(tan(cos(sin((x))))))-128/365.25*x^3)`.



<br>

--------------------------------------------------------------------------------

<br>



```{r sqrt2}
x <- sqrt(2)
x

x.tr <- exp(asin(tan(cos(sin((x)))))) - 128/365.25 * x^3
x.tr
```



<br>

--------------------------------------------------------------------------------

<br>



# R Chunks

```{r SANDBOX, eval = FALSE, echo = FALSE}
# Develop your
# R code
# here
```



<br>

--------------------------------------------------------------------------------

<br>



<!-- The chunk option "echo = FALSE" and "include = FALSE" prevent code and results from appearing in the output. knitr runs the code in the chunk, and the results can be used by other chunks. -->

```{r knitr-setup, include = FALSE}
library(knitr)
opts_chunk$set(echo = FALSE, include = FALSE)
```

```{r R-setup}
##  More settings and "global variables".
options(show.signif.stars = FALSE)
rnd <- 2   ##  Number of decimals to round.
```



<br>

--------------------------------------------------------------------------------

<br>



# R Tables

```{r Kable, include = TRUE}
iris$noise <- rnorm(n = nrow(iris))
kable(iris[1:10, -5])
```



<br>

--------------------------------------------------------------------------------

<br>



With a caption:

```{r Kable2, include = TRUE}
kable(iris[1:10, -5], digits = 4,
      align = c("llccr"),
      caption = "Tab. 1: First 10 Observations
                 in the Famous Iris Data Set.")
```



<br>

--------------------------------------------------------------------------------

<br>



```{r FlexTable}
library(flextable)

##  Create table, and indicate column names to be included
##  with the argument col_keys (nothing is printed yet).
rt <- regulartable(head(mtcars), col_keys = 
                   c("hp", "wt", "gear", "mpg"))
```



<br>

--------------------------------------------------------------------------------

<br>



Flextable:

```{r FlexTable2, include = TRUE}
##  Give columns proper names in the table.
rt <- set_header_labels(rt, hp = "Horsepower",
                        wt = "Weight",
                        gear = "No. of Gears",
                        mpg = "Miles/Gallon")

##  Make header bold and outcome italic.
rt <- bold(rt, part = "header")
rt <- italic(rt, j = 4)   ##  Make column 4 italic.

##  Adjust widths and heights of cells.
rt <- autofit(rt)
rt
```



<br>

--------------------------------------------------------------------------------

<br>



# R Plots

```{r Sine, include = TRUE}
plot(sin, -pi, 2 * pi)
title(main = substitute(paste("Sine from ", -pi, " to 2", pi)))
```



<br>

--------------------------------------------------------------------------------

<br>



```{r knitr-setup2, include = FALSE}
opts_chunk$set(echo = FALSE, include = FALSE,
               fig.path = "Figures/", dev = "jpeg")
```


```{r Sine2, include = TRUE}
plot(sin, -pi, 2 * pi)
title(main = substitute(paste("Sine from ", -pi, " to 2", pi)))
```



<br>

--------------------------------------------------------------------------------

<br>



```{r SineSmall, include = TRUE, fig.height = 3, fig.width = 3}
plot(sin, -pi, 2 * pi)
```



<br>

--------------------------------------------------------------------------------

<br>



```{r Cosine, include = TRUE, fig.cap = "Fig. 2: A cosine curve."}
plot(cos, -pi, 2 * pi)
```



<br>

--------------------------------------------------------------------------------

<br>



# Line Numbers for Code Blocks

Line numbers for code can be added.

In the header of the document, a syntax highlight theme needs to be provided:

    output:
      html_document:
        highlight: tango

<br>

In the chunks, the options `echo` and `include` need to be set to `TRUE`, even if there is no output.



<br>

--------------------------------------------------------------------------------

<br>



Code is displayed like this:

```{r DataCars, echo = TRUE, include = TRUE, attr.source = ".numberLines"}
##  Load the data set.
data(cars)

##  Transform the var. 'speed'.
cars$speed2 <- cars$speed^2
```

The numbers start with 1 in each code block.

```{r DataAnalysis, echo = TRUE, include = TRUE, attr.source = ".numberLines"}
fm <- lm(dist ~ 1 + speed + speed2, data = cars)
#plot(fm)
summary(fm)
```



<br>

--------------------------------------------------------------------------------

<br>



# Commenting-out R Code

The square root of 2 (i.e., `r sqrt(2)`) has many decimals.

```{r SqrtOf2, echo = TRUE, include = TRUE}
y <- 2
y.sqrt <- sqrt(2)
c("y" = y, "Sqrt of y" = y.sqrt)
```


<br>

The square root of 2 <!--(i.e., `r sqrt(2)`)--> has many decimals.

<!--
```{r SqrtOf2-2, echo = TRUE, include = TRUE}
y <- 2
y.sqrt <- sqrt(2)
c("y" = y, "Sqrt of y" = round(y.sqrt, 4))
```
-->

<br>

Use the `#` and `eval = FALSE`:

The square root of 2 <!--(i.e., `r #sqrt(2)`)--> has many decimals.

<!--
```{r SqrtOf2-3, eval = FALSE, echo = TRUE, include = TRUE}
y <- 2
y.sqrt <- sqrrt(2)  <--- NOW ALLOWS FOR ERRORS AND WRONG SYNTAX !!!
c("y" = y, "Sqrt of y" = round(y.sqrt, 4))
```
-->

Hic finis.



<br>

--------------------------------------------------------------------------------

<br>



# R Code in Chunk Options

```{r PlotSettings}
##  Settings for HTML.
fig.h <- 4; fig.w <- 6; fig.scale <- 1

##  Explicit settings for PDF.
#fig.h <- 8; fig.w <- 12

##  Or using a scaling factor.
fig.scale <- 1.5
```


```{r PlotAirquality, include = TRUE, fig.height = fig.h * fig.scale, fig.width = fig.w * fig.scale, fig.cap = paste0("The plot is based on ", nrow(na.omit(airquality[,c("Temp","Ozone")])), " (of ", nrow(airquality), ") measurements (", sum(is.na(airquality$Ozone)), " missing values in var. `Ozone`, ", sum(is.na(airquality$Temp)), " missing values in var. `Temp`).")}
plot(Ozone ~ Temp, data = airquality, ylab = "Ozone conc. (in ppb)", xlab = "Temperature (in ºF)", main = "New York (May to September 1973)")
```







